---
title: 'CA #5'
author: "Victoria Kincaid"
date: "9/24/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(nycflights13)
library(fivethirtyeight)
library(scales)
```

```{r, echo=FALSE}

# Stock_pricesNT <- matrix(c(173.55,174.90,174.34,172.61,171.42,170.04), ncol = 3, byrow = TRUE)
#   colnames(Stock_pricesNT) <- c("Boeing Stock Price", "Amazon Stock Price", "Google Stock Price")
#   rownames(Stock_pricesNT) <- c("2009-01-01", "2009-01-02")
#   Stock_pricesNT <- as.table(Stock_pricesNT)
# Stock_pricesNT
# 
# 
# Stock_pricesT <- Stock_pricesNT %>%
#   pivot_longer(names_to = "Stock Name",
#                values_to = "Stock Price",)
# ```
# THIS DID NOT WORK SO ATTEMPTING TO IMPORT
```

Table 4.1
```{r}
library(readxl)
Table4_1 <- read_excel("ca5scrap.xlsx")
format(Table4_1, nsmall = 2)

knitr::kable(tibble::data_frame(Table4_1))
```


Table 4.2
```{r}
Table4_2 <- Table4_1 %>%
    rename(Boeing = `Boeing stock price`, Amazon = `Amazon stock price`, Google = `Google stock price`) %>%
    pivot_longer(names_to = "Stock Name", 
               values_to = "Stock Price", 
               cols = -Date)
format(Table4_2, nsmall = 2)

knitr::kable(tibble::data_frame(Table4_2))
```


Table 4.3
```{r}
Weather <- c("Sunny", "Overcast")

Table4_3 <- Table4_1 %>%
  select(Date, `Boeing stock price`) %>%
  rename('Boeing Price' = `Boeing stock price`)

Table4_3$new_col <- Weather

names(Table4_3)[3] <- 'Weather'

format(Table4_3, nsmall = 2)

knitr::kable(tibble::data_frame(Table4_3))
```


```{r}
# Shoutout to 
# https://github.com/yihui/knitr/issues/1606
# for figuring out why my NUM in R were becoming DBL when knitting
```

